Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-07-24 paper-correlations.tex
On C0.5 criterion

>>>>

The interface between phases must not change very rapidly for the edge filter to
work correctly. Therefore, the algorithms for surface functions require input
images to be in good resolution. A criterion for goodness can be expressed with
$C_{\alpha}$ parameter. Let $\alpha \in [0, 1]$ and $f(x)$ be your
(band-limited) input image ($x \in \mathbb{R}^2$ or $\mathbb{R}^3$). We define
$C_\alpha$ as follows:
\begin{align*}
  f_0(x) &= f(x) - \langle f(x) \rangle \\
  C_\alpha &= \frac{\int_{-\alpha\omega}^{\alpha\omega} |\hat{f_0}(z)|^2
    dz}{\int_{-\omega}^{\omega} |\hat{f_0}(z)|^2 dz}
\end{align*}
where $\hat{f_0}$ is a Fourier transform of $f_0$ and $\omega$ is a folding
frequency which depends only on resolution of the image. Our criterion is that
if $C_{0.5} > 0.97$ then the image is suitable for our algorithms which compute
$F_{ss}$ and $F_{sv}$.
